\section{Experimental Protocol}
\label{sec:experiments}

\subsection{Questions and Benchmark}

The experiments answer three questions. First, when frozen visual evidence is
held fixed, does index-consistent projection improve anomaly detection?
Second, does label-free inspection confirm the predicted support-graph
failure? Third, how does the repaired screen compare descriptively with the
closest 2026 visual screen under its published benchmark taxonomy?

We evaluate all 492 univariate series used by the eleven subdatasets in
VLM4TS Table~1~\cite{he2026vlm4ts}. The suite contains five NAB groups
(Artificial, AWS, AdExchange, Traffic, and Tweets), two NASA spacecraft
groups (MSL and SMAP), and four Yahoo S5 groups (A1--A4). Their respective
series counts are 6, 17, 5, 7, 10, 27, 53, 67, 100, 100, and 100. These
sources span synthetic events, cloud and application telemetry, spacecraft
sensor channels, and Web-service time series. Each metric is first averaged
over series within a subdataset and then equally over the eleven subdatasets,
preventing the four 100-series Yahoo groups from dominating the aggregate.

\subsection{Comparison Boundary and Selection Provenance}

The causal comparison uses two score arms produced from identical frozen
token caches. \textsc{REL-U} applies the released shifted-membership
projection. \textsc{IHP} is the prespecified \textsc{IDX-U} component arm and
replaces only that projection with Eqs.~\eqref{eq:literal_incidence} and
\eqref{eq:harmonic_pullback}. Both arms share rendered windows, CLIP tokens,
multiscale pooling, visual memory, token matching, scale fusion, timestamp
stitching, and the evaluator. F1-max selects its maximizing operating point
separately for each arm; AUPRC and VUS-PR are threshold-free. Their paired
difference therefore isolates score changes caused by the token-to-grid
projection, not a representation or capacity change.

IHP was selected after the registered composite Coordinate Envelope failed
its gate on the same 492 series. It was not created or retuned after that
failure, but this promotion is still a post-selection step. Consequently, the
hierarchical bootstrap intervals below quantify sampling variability and are
not adjusted for arm selection; we do not interpret them as confirmatory
post-selection inference.

The external reference is the ViT4TS screening row reported in VLM4TS
Table~1. We transcribe its eleven F1-max values and reported
equal-subdataset mean; we neither call them a local reproduction nor use them
for paired inference. Full VLM4TS reports 0.659 F1-max, but it includes a
separate language-model verification stage and is therefore only external
system context for the locally evaluated screen.

\subsection{Metrics and Uncertainty}

We report F1-max for compatibility with VLM4TS Table~1. The primary
same-cache evidence uses area under the precision--recall curve (AUPRC) and
the range-aware volume under the precision--recall surface (VUS-PR)
\cite{paparrizos2022vus}, which do not depend on a selected anomaly threshold.
Higher values are better for all three metrics.

We use 10,000 hierarchical paired bootstrap replicates. Each replicate first
samples the eleven subdatasets with replacement and then samples paired series
within every selected subdataset. Percentile 95\% intervals are reported for
the IHP-minus-\textsc{REL-U} difference with seed 2027. As noted above, these
intervals are unadjusted for the component-arm selection step.

\subsection{Implementation, Offline Protocol, and Label Isolation}

The frozen vendor repository is fixed at commit
\path{8ab8c16414eb2c1a861dfc3e76f458180035a879}. The screen uses CLIP
ViT-B/16 with $224\times224$ images and a $14\times14$ base-token grid.
Windows have length 240 and step 60. The released preprocessing detrends each
complete series and applies full-series min--max scaling; visual memory is the
token-wise median over all windows of the evaluated series. The score
evaluator retains the released exponentially weighted moving average span
$\max(1,\lfloor0.01T\rfloor)$ and alpha grid
$\{0.1,0.01,0.001\}$, and VUS uses maximum range window 100. Yahoo S5 is
drawn from the verified mirror revision
\path{ea89753da2b451928436adb333c7a2e892461c7d}.

Embedding extraction ran with Python~3.10, PyTorch~2.9.1+cu128, and one
NVIDIA RTX~4090 with 24~GB of memory. IHP itself is deterministic and has no
hyperparameter, training epoch, or dataset-specific choice. It operates on
already computed token costs and requires zero additional encoder passes.
Because preprocessing and memory use the complete evaluated series, the
protocol is label-free but offline and transductive, not streaming. Labels are
loaded only after complete score files have been written; neither cache
construction nor either projection arm can access them.
