\section{Introduction}

Training-free anomaly screening is attractive for heterogeneous telemetry,
provided that detected evidence can be localized to the measurements that
generated it. Cloud services, networked applications, spacecraft, and sensor
systems produce signals with different normal regimes and failure patterns;
maintaining a separately trained detector for every source is costly. Recent
work therefore explores both reliable cross-domain benchmarks
\cite{liu2024elephant} and telemetry-specific unsupervised detectors
\cite{dong2025blade}. Yet deployment requires more than a strong anomaly
score: an operator must return that score to the correct timestamp for alert
ranking and diagnosis.

Frozen vision representations provide a promising alternative to
dataset-specific training. VLM4TS converts a time-series window to a line
image, uses its ViT4TS stage to screen candidate anomalies with frozen CLIP
features, and can then invoke a vision--language model for verification
\cite{he2026vlm4ts,radford2021clip}. The screening stage builds multiscale
visual tokens, compares them with a visual memory, projects the resulting
token costs to a common image grid, and finally maps image columns back to
time. This design makes the token-to-grid projector a semantic interface:
even perfectly informative frozen tokens cannot localize an anomaly if their
inverse coordinate map assigns evidence to a different cell.

We find that this coordinate contract is inconsistent in the released
projector. The supplied pooling memberships contain zero-based flattened
base-cell indices, but the projector queries whether each set contains
$i+1$. At each pooled scale on the $14\times14$ grid, 195 output queries find
support, yet every one is displaced by one flattened cell. Thirteen of these
queries wrap across row boundaries, and the terminal query has no support. A
finite-value fallback then turns that structural hole into a zero anomaly
contribution. The issue is therefore not the syntactic size of an index
change: the shifted graph assigns multiscale evidence to incorrect cells and
makes the projection incomplete for every rendered window.

We address this interface with Index-Consistent Harmonic Projection (IHP), a
minimal coordinate-contract repair. IHP reconstructs the literal
token-to-cell graph specified by the zero-based memberships and then applies
the unchanged ViT4TS harmonic projector on that corrected support. The
harmonic mean itself is not presented as new; the contribution is a complete
projection defined on the coordinate convention that generated the masks.
The renderer, encoder, all-window visual memory, token matching, scale fusion,
and timestamp stitching remain frozen, so IHP adds neither learned capacity
nor another backbone pass.

This narrow intervention enables two complementary evaluations. A label-free
certificate tests whether the predicted displacement, row wraps, and hole
exist and whether
literal incidence restores complete coverage. A same-cache comparison then
holds every visual token and downstream operation fixed while replacing only
the projection. Across 492 series and all eleven NAB, NASA, and Yahoo
subdatasets, IHP increases equal-subdataset F1-max, AUPRC, and VUS-PR over the
released-coordinate control by 0.0267, 0.0218, and 0.0102. Unadjusted
hierarchical intervals exclude zero for AUPRC and VUS-PR, whereas the F1-max
interval crosses zero. As external context, IHP obtains 0.662 F1-max versus
the paper-reported ViT4TS value of 0.612 and is higher on 9/11 subdatasets;
this external comparison is descriptive, not paired.

The contributions are:
\begin{itemize}
  \item We formalize index consistency at the multiscale mask-to-grid
  interface and certify that all 195 valid pooled-scale queries are shifted,
  including 13 row wraps, while the terminal query is unsupported.
  \item We derive and implement a complete index-consistent repair for the
  ViT4TS mask-to-grid interface, without changing the inherited harmonic
  reducer or any learned component.
  \item We evaluate the intervention on 492 series from eleven telemetry
  subdatasets, separating an explicitly paper-reported external comparison
  from a same-cache causal control with hierarchical uncertainty estimates.
\end{itemize}
