\section{Related Work}

\subsection{Numerical and Pretrained Time-Series Anomaly Detection}
Recent time-series anomaly detection (TSAD) methods improve the detector itself
through patch representations, calibrated normal spaces, or richer temporal
interactions.  PaAno learns efficient patch-level representations, DoKnowAD
refines normal representations with domain knowledge, and IGAD introduces a
parameter-free idempotent reconstruction rule~\cite{park2026paano,xing2026doknowad,sun2025igad}.
CrossAD and ScatterAD model cross-scale, cross-window, or temporal--topological
structure~\cite{li2025crossad,yin2025scatterad}, whereas DADA and CATCH pursue
generalization through pretrained bottlenecks or frequency-aware channel
modeling~\cite{shentu2025dada,wu2025catch}.  A recent analysis further shows
that temporal understanding and precise localization remain difficult for
large language models~\cite{park2025llmtsad}.  These advances change learned
representations, reconstruction objectives, or detector semantics.  IHP
instead addresses the inverse interface after a frozen visual detector has
already produced multiscale token costs.

\subsection{Visual and Multimodal TSAD}
Visual encodings provide a second route to transferable TSAD.  Recent systems
evaluate multimodal language models on rendered time series, learn visual
conversions for anomaly recognition, or align visual evidence with temporal
locations~\cite{xu2026visualtimeanomaly,wang2026vits,yang2026vetime}.  The
closest system is VLM4TS, whose ViT4TS screening stage renders windows, extracts
frozen visual features, matches them to a visual memory, and projects
multiscale token costs to a dense field before reducing that field to a time
series~\cite{he2026vlm4ts}.  Its optional second stage uses a vision--language
model to refine candidate intervals.  Our evaluated scope is deliberately
narrower: we retain the released renderer, frozen encoder, memory, matching,
fusion, and stitching, and repair only the multiscale screen's mask-to-grid
projection.  VETime is a concurrent preprint that inverts a periodic visual
layout with learned alignment~\cite{yang2026vetime}; IHP instead uses the
literal incidence already supplied by the frozen projector and adds no learned
alignment.

\subsection{Training-Free Localization and Grid Consistency}
Training-free visual anomaly detectors demonstrate that strong frozen features
can support dense localization through carefully chosen geometric operators.
UniVAD matches component-aware patch features, LogSAD combines vision--language
evidence, and SubspaceAD models a normal feature subspace without training a new
backbone~\cite{gu2025univad,zhang2025logsad,lendering2026subspacead}.
UniFormaly additionally studies background masking and top-ratio aggregation
for task-agnostic visual anomaly detection~\cite{lee2026uniformaly}.  These
methods operate on spatial images and do not define how a time-series renderer's
pooled memberships must be pulled back to the base token grid.

Grid geometry is not innocuous.  Alias-Free ViT and shift-equivariant ViT
identify tokenization, patch merging, attention, and positional encoding as
sources of sensitivity to translations~\cite{michaeli2025aliasfreevit,rojasgomez2024shiftvit}.
They redesign the visual architecture to control input shifts; IHP leaves the
backbone unchanged and enforces a different property---literal incidence
between already-computed pooled tokens and output cells.  Thus, the relevant
gap is not another feature encoder or anomaly reducer, but an explicit and
complete coordinate contract for the inverse multiscale projection.

\subsection{Telemetry Monitoring and Evaluation}
Reliable telemetry anomaly detection requires both heterogeneous benchmarks
and deployment-aware evaluation.  TSB-AD consolidates diverse anomaly families,
while VUS supplies range-aware, threshold-independent metrics~\cite{liu2024elephant,paparrizos2022vus}.
Recent MSN work studies behavior-level network-service anomalies and unlabeled
distribution drift~\cite{dong2025blade,tan2025generative}, underscoring the
importance of stable screening across evolving sensing and networking data.
These works motivate our telemetry setting but are not quantitative comparators.
Taken together, the literature develops stronger representations, multimodal
reasoning, and dense visual localization.  Our narrower gap lies in the
released ViT4TS mask-to-grid interface: IHP makes its supplied multiscale
support graph explicit and restores complete base-grid support before the
unchanged harmonic aggregation.
